An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-26 VLDB2026/main.tex
1

	\textcolor{orange}{For large-scale dataset, DSG only supports single-threaded construction, resulting in the longest build time.}

	\textit{\textbf{Index size.}} 
	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index size. Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
	%On low-dimensional datasets (Deep, YT-Audio),

>>>>

	\textcolor{orange}{For large-scale dataset, ACORN-1 achieves the fastest index construction. This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors.DSG only supports single-threaded construction, resulting in the longest build time.}

	\textit{\textbf{Index size.}} 
	As shown in Figure~\ref{fig:rangeFilter_index_size_mb}, Among all algorithms, Faiss has the smallest index size. Because IVF only adds centroid data and partition information to the vector dataset, the IVF index is only slightly larger than the vector dataset.
